Model Finding for Recursive Functions in SMT

### 2015-04-29 tex/main.tex
uniformized affiliation
more

\author {Andrew Reynolds\inst{1} \and Jasmin Christian Blanchette\inst{2,3} \and Cesare Tinelli \inst{4}}
\authorrunning {A. Reynolds \and J. C. Blanchette \and C. Tinelli}
\institute{
\'Ecole Polytechnique F\'ed\'erale de Lausanne (EPFL), Switzerland
\and
Inria Nancy \& LORIA, Villers-l\`es-Nancy, France
\and
Max-Planck-Institut f\"ur Informatik, Saarbr\"ucken, Germany
\and
Department of Computer Science, The University of Iowa 
}

@@

\section{Introduction}
\label{sec:introduction}
To do.

@@

Leon, Nitpick, others?

>>>>

\author {Andrew Reynolds\inst{1} \and Jasmin Christian Blanchette\inst{2,3} \and Cesare Tinelli \inst{4}}
\authorrunning {A. Reynolds \and J. C. Blanchette \and C. Tinelli}
\institute{
\'Ecole Polytechnique F\'ed\'erale de Lausanne (EPFL), Switzerland
\and
Inria Nancy \& LORIA, Villers-l\`es-Nancy, France
\and
Max-Planck-Institut f\"ur Informatik, Saarbr\"ucken, Germany
\and
Department of Computer Science, University of Iowa, USA
}

@@

\section{Introduction}
\label{sec:introduction}

  * why model finding?
  * but SMT solvers better at proving
    * a single universal quantifier in an axiom is enough to put it off track
      (``maybe unsat'')

  * quantifiers in recursive fun defs

  * intuitively, finite quantification suffices:
    * if we make sure all needed values are there
    * if well-founded (assumed!)

  * nasty example (not well-founded)
    * f x = f x + 1

  * how we do it

  * show that it works also for example with weird recursion schemes

@@

Alloy (and Alloy idiom by Kuncak \& Jackson)
The model finder for KIV based on Alloy
Nitpick
Leon
